Adaptive Algorithms Employing Continuous Linear Functionals

### 2018-08-14 AutoAlgorithmLinearFunctionalDataVerC.tex
tweaked notation at beginning

\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:  
\begin{subequations}\label{probDef}
\begin{gather}
f = \sum_{i\in \bbN} \widehat{f}_i u_i \in \calF, \qquad 
\DHJRnorm[\calF]{f}=\DHJRbignorm[2]{(\widehat{f}_i\big)_{i\in \bbN}}, \\
g = \sum_{i\in \bbN} \widehat{g}_i v_i \in \calG, \qquad \DHJRnorm[\calG]{g}=\DHJRbignorm[2]{(\widehat{g}_i\big)_{i\in \bbN}}.
\end{gather}
Let these two bases be chosen by the singular value decomposition so that the linear solution operator, $S:\calF \to \calG$, satisfies
\begin{gather}
S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i=1}^n \lambda_i \widehat{f}_i v_i, \\
\lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
\DHJRnorm[\calF \to \calG]{S} := \sup_{f \ne 0} \frac{\DHJRnorm[\calG]{S(f)}}{\DHJRnorm[\calF]{f}} = \lambda_1.
\end{gather}
\end{subequations}
This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.  We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.

>>>>

\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i \in \bbN}$, let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i\in \bbN}$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:  
\begin{subequations}\label{probDef}
\begin{gather}
f = \sum_{i\in \bbN} \widehat{f}_i u_i \in \calF, \qquad 
\DHJRnorm[\calF]{f}=\DHJRbignorm[2]{(\widehat{f}_i\big)_{i\in \bbN}}, \\
g = \sum_{i\in \bbN} \widehat{g}_i v_i \in \calG, \qquad \DHJRnorm[\calG]{g}=\DHJRbignorm[2]{(\widehat{g}_i\big)_{i\in \bbN}}.
\end{gather}
Let these two bases be chosen by the singular value decomposition so that the linear solution operator, $S:\calF \to \calG$, satisfies
\begin{gather}
S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i=1}^n \lambda_i \widehat{f}_i v_i, \\
\lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
\DHJRnorm[\calF \to \calG]{S} := \sup_{f \ne 0} \frac{\DHJRnorm[\calG]{S(f)}}{\DHJRnorm[\calF]{f}} = \lambda_1.
\end{gather}
\end{subequations}
This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.  We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
